---
title: "Homework 2"
author: "Graham Miotke"
date: "9/27/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(nycflights13)
```

```{r}
flights
```

Question 1!

```{r}
flights%>%
  filter(is.na(dep_time))
```

8,255 flights have a missing departure time. The other missing variables from these flights are departure delay, arrival time, arrival delay & air time. These observations most likely represent cancelled flights. 

Question 2!

```{r}
flights%>%
  mutate(dep_time = (dep_time%/%100)*60 + dep_time%%100,
         sched_dep_time = (sched_dep_time%/%100)*60 + sched_dep_time%%100,
         arr_time = (arr_time%/%100)*60 + arr_time%%100,
         sched_arr_time = (sched_arr_time%/%100)*60 + sched_arr_time%%100)
```

Question 3!

```{r}
flights%>%
  group_by(month,day)%>%
  mutate(cancelled = is.na(dep_time))%>%
  summarize(avg_delay = mean(dep_delay, na.rm = T),
            number_flights = n(),
            number_cancelled = sum(cancelled),
            proportion = number_cancelled/number_flights)%>%
  ggplot(aes(x=proportion, y = avg_delay))+geom_point()
```

It does not seem as if there is a pattern in the number of cancelled flights. Based on the graph, it also seems as if there is not a significant relation between the average delay and the proportion of flights cancelled on that day.
